\section{Research Experience}

\cventry{2015--Present}{Graduate Research Fellow}{Columbia Water Center}{Columbia University Department of Earth and Environmental Engineering}{New York, NY}{
    Developed methods to understand the ways in which information and uncertainties about the future shape system design and investment in water systems and climate adaptation.
    Identified specific flood drivers in the Ohio River Basin and Lower Paraguay River Basin at daily and sub-seasonal time scales.
}

\cventry{2014--2015}{Undergraduate Research Assistant}{Lab of Jaehong Kim, Department of Chemical and Environmental Engineering}{Yale University}{New Haven, CT}{
    Used CAD, 3D printing, and circuit design to prototype and measure UVC-LED technology for portable water treatment.
    Evaluated technical and economic viability of UV-C disinfection as a function of LED cost.
}

\cventry{2014}{Visiting Student Researcher}{Water and Climate Risks Lab}{Hydraulic and Environmental Engineering Department, Universidade Federal do Ceará}{Fortaleza, Brazil}{
    Conducted bottom-up drought vulnerability assessment of rural drinking water systems in semi-arid northeastern Brazil.
    Used field data and rainfall data to demonstrate that federal investment in rainwater harvesting lessened but did not solve drought vulnerability.
}

\cventry{2013}{Mechanical Design Intern}{DEKA Research and Development}{Manchester, NH}{}{
    Used CAD and 3D printing to evaluate design changes for Slingshot water purification system.
}

\cventry{2012}{Undergraduate Research Assistant}{Lab of Jan Schroers, Department of Mechanical Engineering and Materials Science}{Yale University}{New Haven, CT}{
    Prototyped and conducted measurements of novel bulk metallic glass alloys.
}

\cventry{2012}{Summer Intern}{Ikatú Agua Project}{Fundación Paraguaya}{Asunción, Paraguay}{
    Assessed impact of credit for water system improvement in 19 rural communities.
    Carried out systematic review of program and presented recommendations to foundation leadership.
}