\Header{Talks and Presentations}
\newplace Invited Talks & \textbf{Towards Adaptive Resilience: Decision and Policy Support for Household Flood Risk Management}, \textit{Department of Earth and Environmental Engineering Summer Seminar}, Columbia University. & 2020-08-21 \\
%
& \textbf{Prediction and Implications of Structured Climate Risk for Sequential Adaptation under Deep Uncertainty}, \textit{Center for Climate Risk Management CLIMA Seminar}, the Pennsylvania State University, State College, PA. & 2020-01-29 \\
%
& \textbf{Prediction and Implications of Structured Climate Risk for Sequential Adaptation under Deep Uncertainty}, \textit{Department of Civil and Environmental Engineering}, Rice University, Houston, TX. & 2020-01-27 \\
%
& \textbf{Prediction and Implications of Structured Climate Risk for Sequential Adaptation under Deep Uncertainty}, \textit{Complex Systems Simulation and Optimization Group}, National Renewable Energy Laboratory, Golden, CO. & 2020-01-07 \\
%
& \textbf{Drivers of Extreme Rainfall: Atmospheric Circulation Patterns and Regional Intense Rainfall in the Ohio River Basin}, \textit{European Flood Awareness System Group}, European Centre for Medium Range Weather Forecasting, Reading, England. & 2016-09-02\\
%
& \textbf{Understanding the Physical Drivers of Extreme Rainfall for Flood Prediction}, \textit{Oxford Water Network}, Oxford University, Oxford, England. & 2016-08-26 \\
%
\newplace Workshop Presentations & \textbf{Adaptive Resilience through Real Options and Deep Reinforecement Learning}, \textit{Doctoral Consortium on Computational Sustainability}, Carnegie Mellon University, Pittsburgh, PA. Oral Presentation. & 2019-10-18 \\
%
& \textbf{Evaluating Staged Investments in Critical Infrastructure for Climate Adaptation},\textit{Interdisciplinary Ph.D. Workshop in Sustainable Development}, Columbia University,New York, NY. Oral Presentation. & 2019-04-13 \\
%
& \textbf{Robust Adaptation to Multi-Scale Climate Variability}, \textit{The Nexus of Climate Data, Insurance, and Adaptive Capacity}, Asheville, NC. Poster Presentation. & 2018-11-08 \\
%
& \textbf{Extreme Rainfall in Paraguay During the 2015-16 Austral Summer}, \textit{North East Graduate Student Water Symposium}, University of Massachusetts Amherst, Amherst, MA. Oral Presentation. & 2017-09-10 \\
%
& \textbf{Regional Intense Precipitation: Inferences From GCM Atmospheric Circulation Fields},\textit{Modeling Research in the Cloud}, NCAR, Boulder, Colorado. Poster Presentation. & 2017-05-31 \\
%
& \textbf{Statistical-Dynamical Analysis of Climate Projections for Flood Infrastructure Design},\textit{Interdisciplinary Ph.D. Workshop in Sustainable Development 2017}, Columbia University, New York, NY. Oral Presentation. & 2017-04-21 \\
%
& \textbf{Physical Mechanisms and Subseasonal-to-Seasonal Predictability of Persistent Intense Rainfall and Paraguay River Flooding During the Austral Summer 2015/2016}, \textit{Workshop on Subseasonal to Seasonal Predictability of Extreme Weather and Climate}, Columbia University, New York, NY. Poster Presentation. & 2016-12-07 \\