\section{Experience}

%\subsection{Research Experience}

\cventry{2015--Present}{Graduate Student Researcher}{\href{water.columbia.edu}{Columbia Water Center}, Department of Earth and Environmental Engineering, Columbia University}{New York}{}{
Statistical modeling and process-based understanding of extreme precipitation events and flooding
}

\cventry{2014--2015}{Student Researcher}{Universidade Federal do Cear\'{a}, 
Hydraulic and Environmental Engineering Department}{Fortaleza}{Brazil}{
Created computer model to evaluate hydraulic sustainability for two spatial scales. Coupled rainfall-runoff, evaporation, and precipitation models to estimate water levels of small reservoirs in rural areas.
}

%\subsection{Project Experience}

\cventry{2014-2015}{Research Assistant}{Prof. Jaehong Kim}{Yale University}{}{
Researched design and application of UVC-LED technology for water purification. Built lab testing apparatus and cell phone case to house UVC-LEDs.
}

\cventry{2014}{President}{Engineers Without Borders, Yale Undergraduate Chapter}{}{}{
Also Design Lead (2013), Member (2012, 2015). Led 30-member interdisciplinary team through design and construction of rural water supply system for community of \num{2000} in Rohvitangitaa, Cameroon.
}

\cventry{2013}{Mechanical Design Intern}{DEKA Research and Development}{Manchester, NH}{}{
Built and tested Slingshot water purification systems. Advised Slingshot trials in rural Paraguay.
}

\cventry{2012}{Ikat\'{u} Agua Project Intern}{Fundaci\'{o}n Paraguaya}{Asunci\'{o}n}{Paraguay}{
Developed and conducted review of microcredit program to help rural water providers in rural Paraguay make sustainable service improvements. Visited 19 rural communities in 5 states and presented findings.
}