%-----------------WATER RESEARCH EXPERIENCE----------------
\section{Water Research and Project Experience}


\cventry{2014--2015}{Student Researcher}{Federal University of Ceará, Hydraulic and Environmental Engineering Department}{Fortaleza}{Brazil}{Created computer model to evaluate hydraulic sustainability for two spatial scales. Coupled rainfall-runoff, evaporation, and precipitation models to estimate water levels of small reservoirs in rural areas. Authored conference and journal publications.}

\cventry{2011--Present}{--}{Engineers Without Borders, Yale Undergraduate Chapter}{}{}{President (2014), Design Lead and Travel Team Member (2013). Led 30-member interdisciplinary team through five-year design and construction of gravity-fed water system in Rohvitangitaa, Cameroon.}

\cventry{2013}{Mechanical Design Intern}{DEKA Research and Development}{Manchester, NH}{}{Designed and executed test plans to evaluate system components of Slingshot water purification technology. Constructed Slingshot systems and sub-assemblies for testing and evaluation, developed comprehensive failure analysis, and integrated results into system design.}

\cventry{2012}{Ikatú Agua Project Intern}{Fundación Paraguaya}{Asunción}{Paraguay}{Developed and conducted review of the Ikatú Agua microcredit program to help rural water providers in rural Paraguay make sustainable improvements to their service. Visited 19 rural communities in 5 states and presented findings to Fundación Paraguaya and partner organization AVINA.}


%------ OTHER EXPERIENCE-----------------------
\section{Leadership, Service, and Other Experience}

\cventry{2012}{Private Tutor}{}{}{}{High school calculus, chemistry, physics, and Spanish}
\cventry{2014--2015}{College Access Adviser}{Housing Authority of New Haven}{}{}{Designed and led weeklong college access preparation program during winter break}
\cventry{2014}{Undergraduate Liaison}{Yale World Fellows Program}{}{}{Undergraduate contact for Paula Moreno (Colombia)}
\cventry{2012--2014}{Founder and President}{New Haven REACH}{}{}{Created mentoring program to pair Yale undergraduates with New Haven high school seniors going through college application process}
\cventry{2013}{Undergraduate Research Assistant}{Schroers Lab Group}{}{}{Fabricated and investigated properties of Bulk Metallic Glasses}